
\setlength{\parindent}{0cm}
\setlength{\parskip}{0.2cm}
\addtocounter{secnumdepth}{1}
\sloppy



\chapter{Gemoda file documentation}\label{chapter:gfiles}
\section{Introduction}
    This chapter contains detailed documentation of the source code
    implementation of the Gemoda algorithm described in
    Chapter~\vref{chapter:gemoda}.
    The Gemoda software is written in the C programming language
    and
    segmented in such a way as to allow the extension of the
    algorithm to varieties of sequential data that were not
    anticipated by the authors.  Furthermore, where possible the
    code was crafted to be ``object--oriented like'' for maximum
    readability.  The software makes extensive use of the GNU
    Scientific Library~\cite{galassi2003gnu} and the popular Basic Linear
    Algebra Subprograms
    (BLAS)~\cite{blackford2002updated,dongarra2002basicI,dongarra2002basicII}
    to speed--up computationally intensive operations associated
    with the discovery of motifs in three--dimensional protein
    structures and other real--valued data.

    The Gemoda source code is available from \url{http://web.mit.edu/bamel/gemoda}.
    The software includes a number of ``helper'' applications
    for interoperability with common bioinformatics
    tools.

    This software is designed for UNIX--like systems and
     uses the GNU autotools framework for managing
    installation tasks and properly configuring itself for different
    computer architectures.  Gemoda is distributed with a
    \texttt{configure} shell script that tries to guess
    system--dependent variables and to create a ``makefile'' that
    can be used as an input for GNU make.

    To install Gemoda, use the following recipe:
    \begin{enumerate}
      \item Change directories to the folder that contains the ``src''
      directory as a subfolder.  From this location, run the command
      \texttt{./configure}.  To install Gemoda to a nonstandard
      location, use the optional flag \texttt{--prefix=PATH}, where
      \texttt{PATH} is the desired location, such as
      ``/usr/local/software''.
      \item Type \texttt{make} to compile the software using your
      default C compiler, which is specified by the ``CC''
      environment variable.
      \item Type \texttt{make install} to install the software.
    \end{enumerate}
    There are many other options for the \texttt{configure} script.
    To see a list of available options, use the optional flag \texttt{--help}.

    In the following sections of this appendix, I describe in detail
    the organization and design of the Gemoda software.  These
    sections are organized by file and are designed to show the
    dependencies and interactions of different functions.  As
    described in Chapter~\vref{chapter:gemoda}, Gemoda operates in
    three steps: comparison, clustering, and convolution.  The
    software keeps the steps clearly segmented.

\begin{singlespace}
\input{align_8c}
\include{bitSet_8c}
%\include{bitSet_8h}
\include{convll_8c}
\include{convll_8h}
\include{fastaSeqIO_8c}
\include{fastaSeqIO_8h}
\include{gemoda-r_8c}
\include{gemoda-s_8c}
\include{matdata_8h}
\include{matrices_8c}
\include{matrices_8h}
\include{matrixmap_8h}
\include{newConv_8c}
\include{patStats_8c}
\include{patStats_8h}
\include{realCompare_8c}
\include{realCompare_8h}
\include{realIo_8c}
\include{realIo_8h}
\include{spat_8h}
\include{words_8c}
\end{singlespace}

\chapter{Gemoda data structure documentation}\label{chapter:gstructs}

\section{Introduction}
This appendix describes in detail the data structures used in the
Gemoda software, which is described in the appendix on
page~\pageref{chapter:gfiles}.  Although C is not an
object--oriented programming language, we have tried where possible
to use a similar philosophy in our programming.

\begin{singlespace}
\input{structbitGraph__t}
\include{structbitSet__t}
\include{structcnode}
\include{structcSet__t}
\include{structfSeq__t}
\include{structmnode}
\include{structrdh__t}
\include{structsHash__t}
\include{structsHashEntry__t}
\include{structsOffset__t}
\include{structsPat__t}
\include{structsSize__t}
\end{singlespace}
